---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qp4ewc

<!-- badges: start -->
<!-- badges: end -->

The goal of qp4ewc is to provide information that is required as input for the program ECOWEIGHT in a uniform and easy to use way. The needed input is read from different sources is processed and then converted into the format that is required by ECOWEIGHT. 


## Installation

You can install the development version of qp4ewc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sknqualitasag/qp4ewc")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(qp4ewc)
## basic example code
s_path_directory2create <- file.path(tempdir(),"qw4ewc","work")
s_input_file_literature <- system.file("extdata","ewbc","input_literature.txt", package = "qp4ewc")
s_input_file_par <- system.file("extdata","ewbc","input_par_statement.txt", package = "qp4ewc")
s_input_file_calving_statement <- system.file("extdata","ewbc","input_calving_statement.txt", package = "qp4ewc")
s_input_file_calving <- system.file("extdata","ewbc","test","test_zws_muku_gal.csv", package = "qp4ewc")
s_start_date <- 20160101
s_end_date <- 20211231
s_input_file_progeny_flp_statement <- system.file("extdata","ewbc","input_flp_statement.txt", package = "qp4ewc")
s_input_file_flp <- system.file("extdata","ewbc","test","test_zws_muku_flp.csv", package = "qp4ewc")
s_input_file_flp_carcass_matrix_statement <- system.file("extdata","ewbc","input_flp_carcass_matrix_statement.txt", package = "qp4ewc")
s_input_file_price_cow <- system.file("extdata","ewbc","cow_price.txt", package = "qp4ewc")
s_input_file_price_bull <- system.file("extdata","ewbc","bull_price.txt", package = "qp4ewc")
s_input_file_price_heifer <- system.file("extdata","ewbc","heifer_price.txt", package = "qp4ewc")
s_input_file_testedbulls <- system.file("extdata", "ewbc", "input_testedbulls.txt", package = "qp4ewc")
s_input_file_purchasedreplacementheifers <- system.file("extdata", "ewbc", "input_purchasedreplacementheifers.txt", package = "qp4ewc")
pre_process_ewbc_input(ps_sirebreed = "LM",
                       ps_prodsystew = "2",
                       ps_marketchannel = "Natura-Beef",
                       ps_path_directory2create = s_path_directory2create,
                       ps_input_file_literature = s_input_file_literature,
                       ps_input_file_par = s_input_file_par,
                       ps_input_file_testedbulls = s_input_file_testedbulls,
                       ps_input_file_purchasedreplacementheifers = s_input_file_purchasedreplacementheifers,
                       ps_input_file_calving_statement = s_input_file_calving_statement,
                       ps_input_file_calving = s_input_file_calving,
                       ps_start_date = s_start_date,
                       ps_end_date = s_end_date,
                       ps_input_file_progeny_flp_statement = s_input_file_progeny_flp_statement,
                       ps_input_file_flp = s_input_file_flp,
                       ps_input_file_flp_carcass_matrix_statement = s_input_file_flp_carcass_matrix_statement,
                       ps_input_file_price_cow = s_input_file_price_cow,
                       ps_input_file_price_bull = s_input_file_price_bull,
                       ps_input_file_price_heifer = s_input_file_price_heifer,
                       pb_log = TRUE)
```

