---
title: "Explain the function pre_process_ew_input_carcass_data_flp()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explain the function pre_process_ew_input_carcass_data_flp()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the construction of the function `pre_process_ew_input_carcass_data_flp()`. The task of this function is to pre-process the carcass conformation, fat, prices based on different input like flp-data, prices to update the input-parameter-file of ECOWEIGHT.

# Parameters

The parameters needed are:

```{r, echo = TRUE}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "2"
# Marketing channel can be: Natura-Beef, SwissPrimBeef
s_marketingchannel <- "Natura-Beef"
# Path to define from the working directory
s_path_directory2create <- "/Users/skn/muku_Ecoweigth/2022/work"
# Path to input statement for carcass and price
s_input_file_flp_carcass_matrix_statement <- file.path(here::here(),"inst","extdata","input_flp_carcass_matrix_statement.txt")
# Path to flp data file
s_input_file_flp <- "/Users/skn/muku_Ecoweigth/2022/data/zws_muku_flp/test_ANAUCHLMSIOB_zws_muku_flp.csv"
# Date YYYYMMDD used as start date to filter data for calving or carcass
s_start_flp_date <- 20160101
# Date YYYYMMDD used as end date to filter data for calving or carcass
s_end_flp_date <- 20211231
# Path to input with cow price. Based on this example an other file can be created with different input-values.
s_input_file_price_cow <- file.path(here::here(),"inst","extdata","cow_price.txt")
# Path to input with bull price. Based on this example an other file can be created with different input-values.
s_input_file_price_bull <- file.path(here::here(),"inst","extdata","bull_price.txt")
# Path to input with heifer price. Based on this example an other file can be created with different input-values.
s_input_file_price_heifer <- file.path(here::here(),"inst","extdata","heifer_price.txt")
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

# Logfile

At the beginning of the function depending of the setting for `pb_log` and `plogger`, a log-file will be created.

# Statements

To update the ECOWEIGHT input-parameter-files, we need to know the statement as well as the INPUT{n}.TXT (where n represent the number of the input file. This n can be between 01 and 36). The statement is in the second column whereas the input-file is in the first column.

```{r, warning=FALSE, message=FALSE}
tbl_input_statement_flp_carcass <- read_file_input(ps_input_file = s_input_file_flp_carcass_matrix_statement,
                                                   pb_log = b_log)
# Header of the file
tbl_input_statement_flp_carcass[,2]
```

# flp data

In the flp-data-file are the carcass data readed. With the `s_start_flp_date` and `s_end_flp_date` , the time frame of the flp-data to consider is set. The progeny is filtered according to `s_sirebreed` .

```{r, warning=FALSE, message=FALSE}
tbl_flp <- read_file_input_flp(ps_input_file_flp = s_input_file_flp,
                               ps_start_flp_date = s_start_flp_date,
                               ps_end_flp_date = s_end_flp_date,
                               ps_sirebreed = s_sirebreed,
                               pb_log = b_log)
tbl_flp
```

# Number of classes for fleshiness and fat covering

```{r}
# Number of classes for fleshiness
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[11,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[11,2],
                                      ps_value2update = tbl_input_statement_flp_carcass[11,4],
                                      pb_log = b_log)
# Number of classes for fat covering
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[12,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[12,2],
                                      ps_value2update = tbl_input_statement_flp_carcass[12,4],
                                      pb_log = b_log)
```

# Frequency per slaughtercategory

The flp-data are used to calculate the frequencies per slaughtercategory (cow, bull, heifer). 
Always 5 columns representing carcass fat scores 1, 2, 3, 4, 5 and 
9 raws representing carcass conformation scores C, H, T+, T, T-, A, X, XX, XXX.

## Cow

```{r}
# Frequency of the cows are not depending of a marketing channel
freq_mat_cow <- build_freq_conf_fat(ps_input_flp_tibble = tbl_flp,
                                    ps_sex = "F",
                                    ps_marketing_channel = NULL,
                                    ps_flag_cow = TRUE,
                                    pb_log = b_log)
freq_mat_cow
```

```{r}
# For carcass conformation C (use of default value for ps_line4statement2update)
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp_carcass[1,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[1,],4)),collapse = " "),
                                      pb_log = b_log)

```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation H
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[2,],4)),collapse = " "),
                                      ps_line4statement2update = 2,
                                      pb_log = b_log)

```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation T+
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[3,],4)),collapse = " "),
                                      ps_line4statement2update = 3,
                                      pb_log = b_log)
```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation T
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[4,],4)),collapse = " "),
                                      ps_line4statement2update = 4,
                                      pb_log = b_log)
```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation T-
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[5,],4)),collapse = " "),
                                      ps_line4statement2update = 5,
                                      pb_log = b_log)
```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation A
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[6,],4)),collapse = " "),
                                      ps_line4statement2update = 6,
                                      pb_log = b_log)
```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation X
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[7,],4)),collapse = " "),
                                      ps_line4statement2update = 7,
                                      pb_log = b_log)

```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation XX
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[8,],4)),collapse = " "),
                                      ps_line4statement2update = 8,
                                      pb_log = b_log)
```

```{r, warning=FALSE, message=FALSE}
# For carcass conformation XXX
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[1,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[1,2],
                                      ps_value2update = paste0(as.character(round(freq_mat_cow[9,],4)),collapse = " "),
                                      ps_line4statement2update = 9,
                                      pb_log = b_log)
```

## Heifer

```{r}
# Frequency of the heifers of slaughtercategory RG (female and ps_flag_cow = FALSE) in Natura-Beef
freq_mat_heifer <- build_freq_conf_fat(ps_input_flp_tibble = tbl_flp,
                                       ps_sex = "F",
                                       ps_marketing_channel = s_marketingchannel,
                                       ps_flag_cow = FALSE,
                                       pb_log = b_log)
freq_mat_heifer
```

The update for heifer in the input parameter has to be done in a similar way than for cows.

## Bull

```{r}
# Frequency of the bull of slaughtercategory MT and OB (male and ps_flag_cow = FALSE) in Natura-Beef
freq_mat_bull <- build_freq_conf_fat(ps_input_flp_tibble = tbl_flp,
                                     ps_sex = "M",
                                     ps_marketing_channel = s_marketingchannel,
                                     ps_flag_cow = FALSE,
                                     pb_log = b_log)
freq_mat_bull
```

The update for bulls in the input parameter has to be done in a similar way than for cows.

# Prices

## Base price

The prices of Proviande (Wochenpreise für Rindvieh, Woche 8 vom Jahr 2021) are taken for the base price.

```{r}
# base price for cow
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[4,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[4,2],
                                      ps_value2update = tbl_input_statement_flp_carcass[4,4],
                                      pb_log = b_log)

```
```{r}
# average price bull
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[5,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[5,2],
                                      ps_value2update = tbl_input_statement_flp_carcass[5,4],
                                      pb_log = b_log)

```

```{r}
# basis price bull
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[6,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[6,2],
                                      ps_value2update = tbl_input_statement_flp_carcass[6,4],
                                      pb_log = b_log)

```

```{r}
# basis price heifer
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[7,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[7,2],
                                      ps_value2update = tbl_input_statement_flp_carcass[7,4],
                                      pb_log = b_log)

```

## Price coefficient for cow

```{r}
# Price table with combination of carcass fat and conformation for Natura-cows
mat_coeffprice_cow <- read_price_conf_fat(ps_input_file_price = s_input_file_price_cow,
                                          pb_log = b_log)

```

Now, the price coefficient for cow will be updated.

```{r}
# For carcass conformation C
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[8,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[8,2],
                                      ps_value2update = paste0(as.character(round(mat_coeffprice_cow[1,],4)),collapse = " "),
                                      pb_log = b_log)
```

```{r}
# For carcass conformation H
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp_carcass[8,1]),
                                      ps_statement2search = tbl_input_statement_flp_carcass[8,2],
                                      ps_value2update = paste0(as.character(round(mat_coeffprice_cow[2,],4)),collapse = " "),
                                      ps_line4statement2update = 2,
                                      pb_log = b_log)
```

Etc for the different carcass conformation classes as well as for heifers and bulls
