---
title: "Manual Preprocess EWDC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Manual Preprocess EWDC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the construction of the main-function `pre_process_ew_input()`. The task of `pre_process_ew_input()` is to pre-process the input-parameter-files for ECOWEIGHT specific for dairy cattle (EWDC).

# Pre-processing part

Major steps of `pre_process_ew_input()` are 

 1) function `create_directory_scenario()` : the task of this function is to create a directory per scenario with template of input-parameter-file for ECOWEIGHT. 
 
 2) Read file with input from literature research and update input-parameter-file coming from literature of ECOWEIGHT. All these inputs (minerals, straw, water, dung, veterinary cost, cost removing dead animal, cost stock-man hours, fixed cost, semen, gestation length, natural mating, culled, sold, proportion, milk, protein, fat, governmental support, dry matter, net energy, protein, amount, price) are coming from literature research. Further depending of the `s_sirebreed` and `s_dambreed` some values for maturity type of progeny are set as well as the utilisation of the calves (export, fattening). 

 3) function `pre_process_ew_input_calving()` : the task of this function is to pre-process the calving data (by calculating abortion rate, stillbirth rate, calving score proportions, proportion of calves died to 24 hours) to update the input-parameter-file of ECOWEIGHT. In the calving file `s_input_file_calving` are the raw calving data readed. With the `s_start_date` and `s_end_date` , the time frame of the calving data to consider is set. Most of the calculation are done for primiparous (first lactation) as well as multiparous (more than first lactation). Beef-on-dairy requires the same calculations also for purbred dairy animals (these infos are already in the raw calving data).

 4) function `pre_process_ewdc_input_progeny_data_flp()` : the task of this function is to pre-process the progeny data flp (by calculating mean birth weight, mean live weight at slaughter, slaughter age, rearing age, daily gain during rearing and fattening) to update the input-parameter-file of ECOWEIGHT for beef-on-dairy production system. In `s_input_file_flp` are the carcass and progeny raw data as well as calf export `s_input_file_calf` readed. With the `s_start_date` and `s_end_date` , the time frame of this data are set. The pedigree `s_input_file_ped` is needed to get the breed of the sire and the dam, so that we can know if we are looking to purebred beef, purebred dairy or crossbred. The pedigree informations will be merged with the flp-data-file. There are different situation depending on the `s_marketingchannel`.

 
 5) function `pre_process_ewdc_input_carcass_data_flp()` : the task of this function is to pre-process the carcass conformation, fat, prices based on different input like `s_input_file_flp`, prices to update the input-parameter-file of ECOWEIGHT. Number of classes for fleshiness and fat covering are set (here is to say that for fleshiness we consider X, XX, XXX as the same class X due to the preprocessing of the genetic evaluation for carcass traits). Frequency per slaughtercategory (cow, bull (for conventional only MT are considered), heifer, whereas bull and heifer are looked for purebred dairy and crossbred). Then a price week of Proviande is defined to set the base price.

## Parameters 

```{r}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Dam breed can be for beef-on-dairy: HO,BS corresponding to Holstein or Brown Swiss (+Braunvieh) 
s_dambreed <- "HO"
# Production system according to ECOWEIGHT for beef-on-dairy: 4 corresponding to dairy
s_prodsystem <- "4"
# Marketing channel can be: ConventionalBeef, ConventionalVeal, Export corresponding to intensive fattening system for beef or veal or all crossbred calves being sold as calves to the handler
s_marketingchannel <- "ConventionalBeef"
# Path to define from the working directory for beef-on-dairy
s_path_directory2create <- file.path(here::here(),"inst","extdata","ewdc","test","Preprocess_output")
# Path to input from the literature research. Based on this example an other file can be created with different input-value and input-source.
s_input_file_literature <- system.file("extdata","ewdc",paste0("input_literature_",s_dambreed,"_",s_marketingchannel,".txt"), package = "qp4ewc")
# Path to input from the parameter specific for the scenario. Based on this example an other file can be created with different input-value.
s_input_file_par <- system.file("extdata","ewdc","input_par_statement.txt", package = "qp4ewc")
# path to file with input for file 35 for the input-parameter-file for ECOWEIGHT
s_input_file_35 <- system.file("extdata","ewbc","input35_statement.txt", package = "qp4ewc")
# path to file with input for file 36 for the input-parameter-file for ECOWEIGHT
s_input_file_36 <- system.file("extdata","ewbc","input36_statement.txt", package = "qp4ewc")
# Path to specific input for ProdSyst1 for tested bulls (this is only for beef-on-beef needed)
s_input_file_testedbulls <- system.file("extdata","ewbc","input_testedbulls.txt", package = "qp4ewc")
# Path to specific input for ProdSyst3 for replacement progeny heifers (this is only for beef-on-beef needed)
s_input_file_purchasedreplacementheifers  <- system.file("extdata","ewbc","input_purchasedreplacementheifers.txt", package = "qp4ewc")
# Path to input from the calving. Based on this example an other file can be created with different input-values.
s_input_file_calving_statement <- system.file("extdata","ewdc","input_calving_statement.txt", package = "qp4ewc")
# Path to calving data file
s_input_file_calving <- system.file("extdata","ewdc","test","test_zws_muku_gal.csv", package = "qp4ewc")
# Date YYYYMMDD used as start date to filter data for calving or carcass
s_start_date <- 20000101
# Date YYYYMMDD used as end date to filter data for calving or carcass
s_end_date <- 20211231
# Path to input from the progeny flp data. Based on this example an other file can be created with different input-values.
s_input_file_progeny_flp_statement <- system.file("extdata","ewdc","input_flp_statement.txt", package = "qp4ewc")
# Path to flp data file
s_input_file_flp <- system.file("extdata","ewdc","test","test_zws_muku_flp.csv", package = "qp4ewc")
# Path to calf price data file.
s_input_file_calf <- system.file("extdata","ewdc","test","test_calf_data.csv", package = "qp4ewc")
# Path to input statement for carcass and price
s_input_file_flp_carcass_matrix_statement <- system.file("extdata","ewdc","input_flp_carcass_matrix_statement.txt", package = "qp4ewc")
# Path to input with cow price. Based on this example an other file can be created with different input-values.
s_input_file_price_cow <- system.file("extdata","ewdc","cow_price.txt", package = "qp4ewc")
# Path to input with bull price. Based on this example an other file can be created with different input-values.
s_input_file_price_bull <- system.file("extdata","ewdc","bull_price.txt", package = "qp4ewc")
# Path to input with heifer price. Based on this example an other file can be created with different input-values.
s_input_file_price_heifer <- system.file("extdata","ewdc","heifer_price.txt", package = "qp4ewc")
# Path to input with calf price. Based on this example an other file can be created with different input-values
s_input_file_price_calf <- system.file("extdata","ewdc","veal_price.txt", package = "qp4ewc")
# Path to pedigree input file
s_input_file_ped <- system.file("extdata","ewdc","test","test_pedigree.txt", package = "qp4ewc")
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

At the beginning of the function depending of the setting for `pb_log` and `plogger`, a log-file will be created.


## Run pre_process_ew_input() in RStudio

```{r, warning=FALSE, message=FALSE}
pre_process_ew_input(ps_sirebreed = s_sirebreed,
                     ps_dambreed = s_dambreed,
                     ps_prodsystew = s_prodsystem,
                     ps_marketchannel = s_marketingchannel,
                     ps_path_directory2create = s_path_directory2create,
                     ps_input_file_literature = s_input_file_literature,
                     ps_input_file_par = s_input_file_par,
                     ps_input_file_35 = s_input_file_35,
                     ps_input_file_36 = s_input_file_36,
                     ps_input_file_testedbulls = s_input_file_testedbulls,
                     ps_input_file_purchasedreplacementheifers = s_input_file_purchasedreplacementheifers,
                     ps_input_file_calving_statement = s_input_file_calving_statement,
                     ps_input_file_calving = s_input_file_calving,
                     ps_start_date = s_start_date,
                     ps_end_date = s_end_date,
                     ps_input_file_progeny_flp_statement = s_input_file_progeny_flp_statement,
                     ps_input_file_flp = s_input_file_flp,
                     ps_input_file_calf = s_input_file_calf,
                     ps_input_file_flp_carcass_matrix_statement = s_input_file_flp_carcass_matrix_statement,
                     ps_input_file_price_cow = s_input_file_price_cow,
                     ps_input_file_price_bull = s_input_file_price_bull,
                     ps_input_file_price_heifer = s_input_file_price_heifer,
                     ps_input_file_price_calf = s_input_file_price_calf,
                     ps_input_file_ped = s_input_file_ped,
                     pb_log = b_log)
```

The input-files are now ready to execute ECOWEIGHT for dairy cattle (EWDC). This need to be done separately and is not part of the package qp4ewc.
As soon as we have the result file of ECOWEIGHT for dairy cattle (in the vignette *2_Manual_Postprocess_EWDC* some test-file are already available to allow to proceed to the post-processing part), we can run the post-processing part to extract economic weights and population means.
