---
title: "7_Overview_scenari"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{7_Overview_scenari}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about how to get an overview of all the scenario producted with `post_process_ewdc_output()`. 

# Parameters 

```{r,warning=FALSE,message=FALSE}
#Path to files
path_results_files <- system.file("extdata","ewdc","Ecoweight_output", package = "qp4ewc")
# Name of results file from ewdc
s_results_name <- "test"
# Path to output statements from the results file of ewdc
s_output_statement <-  system.file("extdata","ewdc","output_statement.txt", package = "qp4ewc")
# Path to search patterns needed to find correct results 
s_output_search_pattern <- system.file("extdata","ewdc","output_searchpattern.txt", package = "qp4ewc")
# Path to define from the working directory for beef-on-dairy
s_path_directory2create <- file.path(here::here(),"inst","extdata","ewdc","test","Ecoweight_output")
# Path to save table of result 
s_path_extracted_results <- file.path(here::here(),"inst", "extdata", "ewdc", "results")
# Path to genetic standard deviation values 
s_input_genetic_SD <- system.file("extdata","ewdc","input_geneticSD.txt", package = "qp4ewc")
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```


## Step 1:  post-processing reads data from the results files and makes single tables per scenario.

```{r, warning=FALSE, message=FALSE}
results_files <- data.frame(filename = list.files(paste0(path_results_files,"/")))

for(idx in 1:nrow(results_files)){
  s_path_2outputfile <- paste0(path_results_files,"/",results_files[idx,],"/",s_results_name)
  s_scenario <- results_files[idx,]
  scenario_split <- unlist(strsplit(s_scenario, split = "_", fixed = TRUE))
  s_sirebreed <- scenario_split[1]
  s_dambreed <- scenario_split[2]
  s_prodsystew <- scenario_split[3]
  s_marketingchannel <- scenario_split[4]
  post_process_ewdc_output(ps_path_2outputfile = s_path_2outputfile,
                           ps_output_statement = s_output_statement,
                           ps_output_search_pattern = s_output_search_pattern,
                           ps_sirebreed = s_sirebreed,
                           ps_dambreed = s_dambreed,
                           ps_prodsystew = s_prodsystew,
                           ps_marketchannel = s_marketingchannel,
                           ps_path_directory2create = s_path_directory2create,
                           ps_scenario = s_scenario,
                           ps_path_tbl_save = s_path_extracted_results,
                           ps_input_genetic_SD = s_input_genetic_SD,
                           pb_log = b_log)

}
```


## Step 2: post processing combines the single scenario tables into tables sorted by the defined criteria for s_sort_by

### sort by sire: 
```{r}
s_sort_by = "sire_breed"
create_table_results_ewdc(ps_sort_by = s_sort_by,
                          ps_path_results_tbl = s_path_extracted_results,
                          ps_path_save = s_path_extracted_results,
                          pb_log = b_log)

```

### sort by dam:
```{r}
s_sort_by = "dam_breed"
create_table_results_ewdc(ps_sort_by = s_sort_by,
                          ps_path_results_tbl = s_path_extracted_results,
                          ps_path_save = s_path_extracted_results,
                          pb_log = b_log)

```

### sort by marketing channel 
```{r}
s_sort_by = "marketing_channel"
create_table_results_ewdc(ps_sort_by = s_sort_by,
                          ps_path_results_tbl = s_path_extracted_results,
                          ps_path_save = s_path_extracted_results,
                          pb_log = b_log)

```

