---
title: "Explain the function pre_process_ew_input_progeny_data_flp()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explain the function pre_process_ew_input_progeny_data_flp()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, we will try to build unit tests for the differrent sub-function of `pre_process_ew_input_progeny_data_flp()`. 

# Parameters

The parameters needed are:

```{r, echo = TRUE}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "2"
# Marketing channel can be: Natura-Beef, SwissPrimBeef
s_marketingchannel <- "Natura-Beef"
# Path to define from the working directory
s_path_directory2create <- "/Users/skn/muku_Ecoweigth/2022/work"
# Path to input from the progeny flp data. Based on this example an other file can be created with different input-values.
s_input_file_progeny_flp_statement <- file.path(here::here(),"inst","extdata","ewbc","input_flp_statement.txt")
# Path to flp data file
s_input_file_flp <- file.path(here::here(),"inst","extdata","ewbc","test","test_zws_muku_flp.csv")
# Date YYYYMMDD used as start date to filter data for carcass
s_start_flp_date <- 20050101
# Date YYYYMMDD used as end date to filter data for carcass
s_end_flp_date <- 20211231
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```


# Prepare test-read_file_input.R

```{r, warning=FALSE, message=FALSE}
tbl_input_statement_flp <- read_file_input(ps_input_file = s_input_file_progeny_flp_statement,
                                           pb_log = b_log)
```

# Prepare test-read_file_input_flp.R

```{r, warning=FALSE, message=FALSE}
tbl_flp <- read_file_input_flp(ps_input_file_flp = s_input_file_flp,
                               ps_start_flp_date = s_start_flp_date,
                               ps_end_flp_date = s_end_flp_date,
                               ps_sirebreed = s_sirebreed,
                               pb_log = b_log)
#Write output to use intest-read_file_input_flp.R
readr::write_delim(tbl_flp, file = file.path(here::here(),"inst","extdata","ewbc","test","test_tbl_flp.csv"), delim = ";")
```

# Prepare test-get_constants.R

```{r, warning=FALSE, message=FALSE}
l_constants <- get_constants()
l_constants
```

# Prepare test-calculate_mean_birthweight.R

```{r, warning=FALSE, message=FALSE}
# mean birth weight for female in Natura-Beef
female_bw <- calculate_mean_birthweight(ps_input_flp_tibble = tbl_flp,
                                       ps_sex = "F",
                                       ps_marketing_channel = l_constants$value_NaturaBeef,
                                       pb_log = b_log)
female_bw
```

```{r, warning=FALSE, message=FALSE}
male_bw <- calculate_mean_birthweight(ps_input_flp_tibble = tbl_flp,
                                      ps_sex = "M",
                                      ps_marketing_channel = l_constants$value_SwissPrimBeef,
                                      pb_log = b_log)

```

# Prepare test-calculate_mean_liveweight_slaughter.R

```{r, warning=FALSE, message=FALSE}
# mean live weight at slaughter for female in Natura-Beef
livewt_slaughter_f <- calculate_mean_liveweight_slaughter(ps_input_flp_tibble = tbl_flp,
                                                          ps_sex = "F",
                                                          ps_marketing_channel = l_constants$value_NaturaBeef,
                                                          pb_log = b_log)
livewt_slaughter_f
```

```{r, warning=FALSE, message=FALSE}
# mean live weight at slaughter for male in Natura-Beef
livewt_slaughter_m <- calculate_mean_liveweight_slaughter(ps_input_flp_tibble = tbl_flp,
                                                          ps_sex = "M",
                                                          ps_marketing_channel = l_constants$value_SwissPrimBeef,
                                                          pb_log = b_log)
```

# Prepare test-calculate_mean_weaningweight.R

```{r, warning=FALSE, message=FALSE}
# mean weaning weight for female in Natura-Beef
weaningwt_f <- calculate_mean_weaningweight(ps_input_flp_tibble = tbl_flp,
                                            ps_sex = "F",
                                            ps_marketing_channel = l_constants$value_NaturaBeef,
                                            pb_log = b_log)
weaningwt_f
```

```{r}
# mean weaning weight for male in Natura-Beef
weaningwt_m <- calculate_mean_weaningweight(ps_input_flp_tibble = tbl_flp,
                                            ps_sex = "M",
                                            ps_marketing_channel = l_constants$value_SwissPrimBeef,
                                            pb_log = b_log)
weaningwt_m
```

# Prepare test-calculate_mean_weaningage.R

```{r}
weaningage_f <- calculate_mean_weaningage(ps_input_flp_tibble = tbl_flp,
                                          ps_sex = "F",
                                          ps_marketing_channel = l_constants$value_NaturaBeef,
                                          pb_log = b_log)

```

# Prepare test-calculate_mean_slaughterage.R

```{r}
# mean slaughter ag for female in Natura-Beef
slaughterage_f <- calculate_mean_slaughterage(ps_input_flp_tibble = tbl_flp,
                                              ps_sex = "F",
                                              ps_marketing_channel = l_constants$value_NaturaBeef,
                                              pb_log = b_log)
slaughterage_f
```

# Prepare test-calculate_dailygain.R

```{r}
# Mean daily gain for female from weaning to slaughter
dailygain_f <- calculate_dailygain(pv_mean_slaughterage = slaughterage_f,
                                   pv_mean_weaningage = weaningage_f,
                                   pv_mean_livewt_atslaughter = livewt_slaughter_f,
                                   pv_mean_weaningwt = weaningwt_f,
                                   pb_log = b_log)
dailygain_f
```

# Prepare test-calculate_extrapolated_weaningweight.R

```{r}
# Extrapolated weight at 300 days for female
weight_300d_f <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_f,
                                                      pv_daily_gain = dailygain_f,
                                                      pv_mean_weaningwt = weaningwt_f,
                                                      pv_t_days = 300,
                                                      pb_log = b_log)
weight_300d_f
```

# Prepare test-calculate_cow_liveweight.R

```{r}
second_calving_wt <- calculate_cow_liveweight(ps_input_flp_tibble = tbl_flp,
                                              ps_second_calvingweight = TRUE,
                                              pb_log = b_log)
```

```{r}
mature_weight_cow <- calculate_cow_liveweight(ps_input_flp_tibble = tbl_flp,
                                              ps_second_calvingweight = FALSE,
                                              pb_log = b_log)
```


# Calculate mature weight bulls

```{r}
bull_mature_weight <- calculate_bull_liveweight(ps_input_flp_tibble = tbl_flp,
                                                pb_log = b_log)
```
