---
title: "Explain the function pre_process_ew_input_progeny_data_flp()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explain the function pre_process_ew_input_progeny_data_flp()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the construction of the function `pre_process_ew_input_progeny_data_flp()`. The task of this function is to pre-process the progeny data flp (by calculating mean birth weight, mean live weight at slaughter, weaning weight, weaning age, slaughter age, daily gain, extrapolate weaning weight) to update the input-parameter-file of ECOWEIGHT.

# Parameters

The parameters needed are:

```{r, echo = TRUE}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "2"
# Marketing channel can be: Natura-Beef, SwissPrimBeef
s_marketingchannel <- "Natura-Beef"
# Path to define from the working directory
s_path_directory2create <- "/Users/skn/muku_Ecoweigth/2022/work"
# Path to input from the progeny flp data. Based on this example an other file can be created with different input-values.
s_input_file_progeny_flp_statement <- file.path(here::here(),"inst","extdata","ewbc","input_flp_statement.txt")
# Path to flp data file
s_input_file_flp <- "/Users/skn/muku_Ecoweigth/2022/data/internship/muku_flp_2015.csv"
# Date YYYYMMDD used as start date to filter data for carcass
s_start_flp_date <- 20150101
# Date YYYYMMDD used as end date to filter data for carcass
s_end_flp_date <- 20220509
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

# Logfile

At the beginning of the function depending of the setting for `pb_log` and `plogger`, a log-file will be created.

# Statements

To update the ECOWEIGHT input-parameter-files, we need to know the statement as well as the INPUT{n}.TXT (where n represent the number of the input file. This n can be between 01 and 36). The statement is in the second column whereas the input-file is in the first column.

```{r, warning=FALSE, message=FALSE}
tbl_input_statement_flp <- read_file_input(ps_input_file = s_input_file_progeny_flp_statement,
                                           pb_log = b_log)
# Head of the statements to update
tbl_input_statement_flp
```

# flp data

In the flp-data-file are the carcass and progeny data readed. With the `s_start_flp_date` and `s_end_flp_date` , the time frame of the flp-data to consider is set. The progeny is filtered according to `s_sirebreed` .

```{r, warning=FALSE, message=FALSE}
tbl_flp <- read_file_input_flp(ps_input_file_flp = s_input_file_flp,
                               ps_start_flp_date = s_start_flp_date,
                               ps_end_flp_date = s_end_flp_date,
                               ps_sirebreed = s_sirebreed,
                               pb_log = b_log)
# Head of flp-data-file
tbl_flp
```

# Different situation depending on the marketingchannel

During the intership of Jessica Gearing, two marketing channel were considered: Natura-Beef and SwissPrimBeef.
Therefore we will have a look especially to the differences in these marketing channels.

Get the constants:

```{r, warning=FALSE, message=FALSE}
l_constants <- get_constants()
l_constants
```

Only the differences between the marketing channel will be highlighted. Otherwise the case of Natura-Beef is taken als example.

## Calculate mean birth weight for female and male

Es gibt leichte Unterschiede zwischen die Werte aus der Funktion und aus dem Praktikum, da in der Funktion wurde hier zusätzlich das Geschlecht vom Kalb kontrolliert.

```{r, warning=FALSE, message=FALSE}
# mean birth weight for female in Natura-Beef
female_bw <- calculate_mean_birthweight(ps_input_flp_tibble = tbl_flp,
                                       ps_sex = "F",
                                       ps_marketing_channel = l_constants$value_NaturaBeef,
                                       pb_log = b_log)
female_bw
```

```{r, warning=FALSE, message=FALSE}
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp[1,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[1,1]),
                                        ps_statement2search = tbl_input_statement_flp[1,2],
                                        ps_value2update = female_bw,
                                        pb_log = b_log)
```


```{r, warning=FALSE, message=FALSE}
# mean birth weight for male in Natura-Beef
male_bw <- calculate_mean_birthweight(ps_input_flp_tibble = tbl_flp,
                                      ps_sex = "M",
                                      ps_marketing_channel = l_constants$value_NaturaBeef,
                                      pb_log = b_log)
male_bw
```

```{r, warning=FALSE, message=FALSE}
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp[2,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[2,1]),
                                        ps_statement2search = tbl_input_statement_flp[2,2],
                                        ps_value2update = male_bw,
                                        pb_log = b_log)
```

## Calculate mean live weight at slaughter for female and male

```{r, warning=FALSE, message=FALSE}
# mean live weight at slaughter for female in Natura-Beef
livewt_slaughter_f <- qp4ewc::calculate_mean_liveweight_slaughter(ps_input_flp_tibble = tbl_flp,
                                                                  ps_sex = "F",
                                                                  ps_marketing_channel = l_constants$value_NaturaBeef,
                                                                  pb_log = b_log)
livewt_slaughter_f
```

```{r, warning=FALSE, message=FALSE}
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp[3,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[3,1]),
                                        ps_statement2search = tbl_input_statement_flp[3,2],
                                        ps_value2update = livewt_slaughter_f,
                                        pb_log = b_log)

```

```{r, warning=FALSE, message=FALSE}
# mean live weight at slaughter for male in Natura-Beef
livewt_slaughter_m <- calculate_mean_liveweight_slaughter(ps_input_flp_tibble = tbl_flp,
                                                          ps_sex = "M",
                                                          ps_marketing_channel = l_constants$value_NaturaBeef,
                                                          pb_log = b_log)
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp[4,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[4,1]),
                                        ps_statement2search = tbl_input_statement_flp[4,2],
                                        ps_value2update = livewt_slaughter_m,
                                        pb_log = b_log)
```

##  Calculate weaning weight for female and male

```{r, warning=FALSE, message=FALSE}
# mean weaning weight for female in Natura-Beef
weaningwt_f <- calculate_mean_weaningweight(ps_input_flp_tibble = tbl_flp,
                                            ps_sex = "F",
                                            ps_marketing_channel = l_constants$value_NaturaBeef,
                                            pb_log = b_log)
weaningwt_f
```

```{r}
# mean weaning weight for male in Natura-Beef
weaningwt_m <- calculate_mean_weaningweight(ps_input_flp_tibble = tbl_flp,
                                            ps_sex = "M",
                                            ps_marketing_channel = l_constants$value_NaturaBeef,
                                            pb_log = b_log)
weaningwt_m
```

##  Calculate weaning age for female and male

```{r}
# mean weaning age for female in Natura-Beef
weaningage_f <- calculate_mean_weaningage(ps_input_flp_tibble = tbl_flp,
                                         ps_sex = "F",
                                         ps_marketing_channel = l_constants$value_NaturaBeef,
                                         pb_log = b_log)
weaningage_f
```

```{r}
# mean weaning age for male in Natura-Beef
weaningage_m <- calculate_mean_weaningage(ps_input_flp_tibble = tbl_flp,
                                          ps_sex = "M",
                                          ps_marketing_channel = l_constants$value_NaturaBeef,
                                          pb_log = b_log)
weaningage_m
```

Whereas the weaning age for Natura-Beef is extrapolated to 300 days,
for SwissPrimBeef is the mean of weaning age of female and male calculated and set to this statement:

```{r}
tbl_input_statement_flp[7,2]
```


##  Calculate slaughter age for female and male

```{r}
# mean slaughter ag for female in Natura-Beef
slaughterage_f <- calculate_mean_slaughterage(ps_input_flp_tibble = tbl_flp,
                                              ps_sex = "F",
                                              ps_marketing_channel = l_constants$value_NaturaBeef,
                                              pb_log = b_log)
slaughterage_f
```

```{r}
# mean slaughter ag for male in Natura-Beef
slaughterage_m <- calculate_mean_slaughterage(ps_input_flp_tibble = tbl_flp,
                                              ps_sex = "M",
                                              ps_marketing_channel = l_constants$value_NaturaBeef,
                                              pb_log = b_log)
slaughterage_m
```

## Calculate daily gain for female and male

```{r}
# Mean daily gain for female from weaning to slaughter
dailygain_f <- calculate_dailygain(pv_mean_slaughterage = slaughterage_f,
                                   pv_mean_weaningage = weaningage_f,
                                   pv_mean_livewt_atslaughter = livewt_slaughter_f,
                                   pv_mean_weaningwt = weaningwt_f,
                                   pb_log = b_log)
dailygain_f
```

```{r}
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp[5,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[5,1]),
                                        ps_statement2search = tbl_input_statement_flp[5,2],
                                        ps_value2update = dailygain_f,
                                        pb_log = b_log)
```


```{r}
# Mean daily gain for male from weaning to slaughter
dailygain_m <- calculate_dailygain(pv_mean_slaughterage = slaughterage_m,
                                   pv_mean_weaningage = weaningage_m,
                                   pv_mean_livewt_atslaughter = livewt_slaughter_m,
                                   pv_mean_weaningwt = weaningwt_m,
                                   pb_log = b_log)
dailygain_m
```

```{r}
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_flp[6,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[6,1]),
                                        ps_statement2search = tbl_input_statement_flp[6,2],
                                        ps_value2update = dailygain_m,
                                        pb_log = b_log)
```

## Extrapolated weaning weight at different days for female and male

Because Natura-Beef has no fattening period. We set the first weighing to 300 days, second to 302 days and third to 304 days.
Whereas for SwissPrimBeef, the first weighing is the mean weaning weight, second extrapolated to 300 days and third to 400 days.

### Specific case for Natura-Beef

Statement for 300 days:
```{r}
tbl_input_statement_flp[7,2]
```

```{r}
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[7,1]),
                                        ps_statement2search = tbl_input_statement_flp[7,2],
                                        ps_value2update = 300,
                                        pb_log = b_log)
```

```{r}
# Extrapolated weight at 300 days for female
weight_300d_f <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_f,
                                                      pv_daily_gain = dailygain_f,
                                                      pv_mean_weaningwt = weaningwt_f,
                                                      pv_t_days = 300,
                                                      pb_log = b_log)
weight_300d_f

update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[8,1]),
                                        ps_statement2search = tbl_input_statement_flp[8,2],
                                        ps_value2update = weight_300d_f,
                                        pb_log = b_log)
```

```{r}
# Extrapolated weight at 300 days for male
weight_300d_m <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_m,
                                                      pv_daily_gain = dailygain_m,
                                                      pv_mean_weaningwt = weaningwt_m,
                                                      pv_t_days = 300,
                                                      pb_log = b_log)
weight_300d_m

update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[9,1]),
                                        ps_statement2search = tbl_input_statement_flp[9,2],
                                        ps_value2update = weight_300d_m,
                                        pb_log = b_log)
```

Statement for 302 days:
```{r}
tbl_input_statement_flp[10,2]
```

```{r}
# extrapolated to 302 days
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[10,1]),
                                        ps_statement2search = tbl_input_statement_flp[10,2],
                                        ps_value2update = 302,
                                        pb_log = b_log)

```

```{r}
# weaning weight at 302 days
weight_302d_f <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_f,
                                                      pv_daily_gain = dailygain_f,
                                                      pv_mean_weaningwt = weaningwt_f,
                                                      pv_t_days = 302,
                                                      pb_log = b_log)
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[12,1]),
                                        ps_statement2search = tbl_input_statement_flp[12,2],
                                        ps_value2update = weight_302d_f,
                                        pb_log = b_log)
weight_302d_m <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_m,
                                                      pv_daily_gain = dailygain_m,
                                                      pv_mean_weaningwt = weaningwt_m,
                                                      pv_t_days = 302,
                                                      pb_log = b_log)
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[13,1]),
                                        ps_statement2search = tbl_input_statement_flp[13,2],
                                        ps_value2update = weight_302d_m,
                                        pb_log = b_log)
```


Statement for 304 days:
```{r}
tbl_input_statement_flp[11,2]
```


```{r}
# extrapolated to 304 days
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[11,1]),
                                        ps_statement2search = tbl_input_statement_flp[11,2],
                                        ps_value2update = 304,
                                        pb_log = b_log)
```

```{r}
# weaning weight at 304 days
weight_304d_f <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_f,
                                                      pv_daily_gain = dailygain_f,
                                                      pv_mean_weaningwt = weaningwt_f,
                                                      pv_t_days = 304,
                                                      pb_log = b_log)
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[14,1]),
                                        ps_statement2search = tbl_input_statement_flp[14,2],
                                        ps_value2update = weight_304d_f,
                                        pb_log = b_log)
weight_304d_m <- calculate_extrapolated_weaningweight(pv_mean_weaningage = weaningage_m,
                                                      pv_daily_gain = dailygain_m,
                                                      pv_mean_weaningwt = weaningwt_m,
                                                      pv_t_days = 304,
                                                      pb_log = b_log)
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[15,1]),
                                        ps_statement2search = tbl_input_statement_flp[15,2],
                                        ps_value2update = weight_304d_m,
                                        pb_log = b_log)
```

# Calculating cow weight after second calving

```{r}
second_calving_wt <- calculate_cow_liveweight(ps_input_flp_tibble = tbl_flp,
                                              ps_second_calvingweight = TRUE,
                                              pb_log = b_log)
```

```{r}
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[16,1]),
                                      ps_statement2search = tbl_input_statement_flp[16,2],
                                      ps_value2update = second_calving_wt,
                                      pb_log = b_log)
```

# Calculate mature cow weight

```{r}
mature_weight_cow <- calculate_cow_liveweight(ps_input_flp_tibble = tbl_flp,
                                              ps_second_calvingweight = FALSE,
                                              pb_log = b_log)
```

```{r}
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[17,1]),
                                      ps_statement2search = tbl_input_statement_flp[17,2],
                                      ps_value2update = mature_weight_cow,
                                      pb_log = b_log)
```

# Calculate mature weight bulls

```{r}
bull_mature_weight <- calculate_bull_liveweight(ps_input_flp_tibble = tbl_flp,
                                                pb_log = b_log)
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_flp[18,1]),
                                      ps_statement2search = tbl_input_statement_flp[18,2],
                                      ps_value2update = bull_mature_weight,
                                      pb_log = b_log)
```

