---
title: "Explain the function create_directory_scenario()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explain the function create_directory_scenario()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the construction of the function `create_directory_scenario()`. The task of this function is to create avdirectory per scenario with template of input-parameter-file for ECOWEIGHT. 

# Parameters

The parameters needed are:

```{r}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Dam breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental for beef-on-beef, or HO,BS corresponding to Holstein or Brown Swiss (+Braunvieh) 
s_dambreed <- "HO"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "4"
# Marketing channel can be: Natura-Beef, SwissPrimBeef, ConventionalBeef, ConventionalVeal
s_marketingchannel <- "ConventionalBeef"
# Path to define from the working directory
s_path_directory2create <- file.path(here::here(),"inst","extdata","ewdc")
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

# Run create_directory_scenario()

```{r}
create_directory_scenario(ps_sirebreed = s_sirebreed,
                          ps_dambreed = s_dambreed,
                          ps_prodsystew = s_prodsystew,
                          ps_marketchannel = s_marketingchannel,
                          ps_path_directory2create = s_path_directory2create,
                          pb_log = b_log)
```

By running the function `create_directory_scenario()` with these parameters is a directory build up such as each scenario corresponds to a directory. In this directory are templates of EWBC (so based on beef cattle, this means that production system 4 is at this stage not considered) copied. With the function `update_input_parameter_file()` of this package can the template with values updated.
