---
title: "Explain the part only from literature"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explain the part only from literature}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the part coming from the literature to update the input-parameter-file of ECOWEIGHT.

# Parameters

The parameters needed are:

```{r, echo = TRUE}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "2"
# Marketing channel can be: Natura-Beef, SwissPrimBeef
s_marketingchannel <- "Natura-Beef"
# Path to define from the working directory
s_path_directory2create <-  file.path(here::here(),"inst","extdata","ewbc")
# Path to input from the literature research. Based on this example an other file can be created with different input-value and input-source.
s_input_file_literature <- file.path(here::here(),"inst","extdata","ewbc","input_literature.txt")
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

# Statements

To update the ECOWEIGHT input-parameter-files, we need to know the statement as well as the INPUT{n}.TXT (where n represent the number of the input file. This n can be between 01 and 36). The statement is in the second column whereas the input-file is in the first column.
All these inputs (minerals, straw, water, dung, veterinary cost, cost removing dead animal, cost stock-man hours, fixed cost, semen, gestation length, natural mating, culled, sold, proportion, milk, protein, fat, governmental support, dry matter, net energy, protein, amount, price) are coming from literature research.

```{r, warning=FALSE, message=FALSE}
tbl_input_literature <- read_file_input(ps_input_file = s_input_file_literature,
                                               pb_log = b_log)
# Examples of the input-statement
tbl_input_literature[,2]
```

Update all the input of ecoweight where the literature inputs are coming from the above file.

```{r, warning=FALSE, message=FALSE}
  for(l in 1:nrow(tbl_input_literature)){
      update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_literature[l,1]),
                                        ps_statement2search = tbl_input_literature[l,2],
                                        ps_value2update = tbl_input_literature[l,4],
                                        pb_log = b_log)
  }
```

