---
title: "Testing the function pre_process_ew_input_calving()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Testing the function pre_process_ew_input_calving()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the construction of the function `pre_process_ew_input_calving()`. The task of this function is to pre-process the calving data (by calculating abortion rate, stillbirth rate, calving score proportions, proportion of calves died to 24 hours) to update the input-parameter-file of ECOWEIGHT.

# Parameters

The parameters needed are:

```{r, echo = TRUE}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Dam breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental for beef-on-beef, or HO,BS corresponding to Holstein or Brown Swiss (+Braunvieh) 
s_dambreed <- "HO"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "4"
# Marketing channel can be: Natura-Beef, SwissPrimBeef, ConventionalBeef, ConventionalVeal
s_marketingchannel <- "ConventionalBeef"
# Path to define from the working directory
s_path_directory2create <-  file.path(here::here(),"inst","extdata","ewdc")
# Path to input from the calving. Based on this example an other file can be created with different input-values.
s_input_file_calving_statement <- file.path(here::here(),"inst","extdata","ewdc","input_calving_statement.txt")
# Path to calving data file
s_input_file_calving <- file.path(here::here(),"inst","extdata","ewbc","test","test_zws_muku_gal.csv")
# Date YYYYMMDD used as start date to filter data for calving
s_start_calving_date <- 20160101
# Date YYYYMMDD used as end date to filter data for calving
s_end_calving_date <- 20211231
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

# Statements

To update the ECOWEIGHT input-parameter-files, we need to know the statement as well as the INPUT{n}.TXT (where n represent the number of the input file. This n can be between 01 and 36). The statement is in the second column whereas the input-file is in the first column.

```{r, warning=FALSE, message=FALSE}
tbl_input_statement_calving <- read_file_input(ps_input_file = s_input_file_calving_statement,
                                               pb_log = b_log)
tbl_input_statement_calving
```

# gal data

In the gal-data-file are the calving data readed. With the `s_start_calving_date` and `s_end_calving_date` , the time frame of the gal-data to consider is set. 

```{r, warning=FALSE, message=FALSE}
tbl_calving <- read_file_input_calving(ps_input_file_calving = s_input_file_calving,
                                       ps_start_calving_date = s_start_calving_date,
                                       ps_end_calving_date = s_end_calving_date,
                                       pb_log = b_log)
```

Most of the calculation are done for primiparous (first lactation) as well as multiparous (more than first lactation).

# Calculate abortion rate

```{r}
# Abortion rate for primiparous
abortrate_prim <- calculate_abortion_rate(ps_input_calving_tibble = tbl_calving,
                                          ps_statement_firstlactation = TRUE,
                                          pb_log = b_log)
abortrate_prim
# Abortion rate for multiparous
abortrate_multi <- calculate_abortion_rate(ps_input_calving_tibble = tbl_calving,
                                           ps_statement_firstlactation = FALSE,
                                           pb_log = b_log)
abortrate_multi
```

```{r}
# if abortion rate = 0, then set a default value coming from the internship of Jessica
if(abortrate_prim == 0){
  abortrate_prim <- unlist(strsplit(tbl_input_statement_calving[1,4]$input_value, split = " "))[1]
}
if(abortrate_multi == 0){
  abortrate_multi <- unlist(strsplit(tbl_input_statement_calving[1,4]$input_value, split = " "))[2]
}
# Build a vector with 10 lactations for abortion rate
value2update_abortrate <- paste0(c(abortrate_prim, rep(abortrate_multi,9)),collapse = " ")
# Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_calving[1,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[1,1]),
                                      ps_statement2search = tbl_input_statement_calving[1,2],
                                      ps_value2update = value2update_abortrate,
                                      pb_log = b_log)
```

# Calculate stillbirth rate

```{r}
# stillbirth rate for primiparous and for easy calving (calving scores 1 and 2)
stillbirthrate_prim_easy <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                      ps_statement_firstlactation = TRUE,
                                                      ps_statement_easycalving = TRUE,
                                                      pb_log = b_log)
stillbirthrate_prim_easy
# stillbirth rate for multiparous and for easy calving (calving scores 1 and 2)
stillbirthrate_multi_easy <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                       ps_statement_firstlactation = FALSE,
                                                       ps_statement_easycalving = TRUE,
                                                       pb_log = b_log)
stillbirthrate_multi_easy
# stillbirth rate for primiparous and for difficult calving (calving scores 3 and 4)
stillbirthrate_prim_difficult <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                           ps_statement_firstlactation = TRUE,
                                                           ps_statement_easycalving = FALSE,
                                                           pb_log = b_log)
stillbirthrate_prim_difficult
# stillbirth rate for multiparous and for difficult calving (calving scores 3 and 4)
stillbirthrate_multi_difficult <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                            ps_statement_firstlactation = FALSE,
                                                            ps_statement_easycalving = FALSE,
                                                            pb_log = b_log)
stillbirthrate_multi_difficult
```

```{r}
# if stillbirth rate = 0, then set a default value coming from the internship of Jessica
if(stillbirthrate_prim_easy == 0){
  stillbirthrate_prim_easy <- unlist(strsplit(tbl_input_statement_calving[2,4]$input_value, split = " "))[1]
}
if(stillbirthrate_multi_easy == 0){
  stillbirthrate_multi_easy <- unlist(strsplit(tbl_input_statement_calving[2,4]$input_value, split = " "))[2]
}
# Build a vector with 10 lactations for stillbirth rate
  value2update_stillbirthrate_easy <- paste0(c(stillbirthrate_prim_easy, rep(stillbirthrate_multi_easy,9)),collapse = " ")
# Update ECOWEIGHT input-file with the calculated stillbirth rates in tbl_input_statement_calving[2,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[2,1]),
                                      ps_statement2search = tbl_input_statement_calving[2,2],
                                      ps_value2update = value2update_stillbirthrate_easy,
                                      pb_log = b_log)


```

# Update calving score parameter inputs
```{r}
# Update ECOWEIGHT input-file with tbl_input_statement_calving[4,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[4,1]),
                                      ps_statement2search = tbl_input_statement_calving[4,2],
                                      ps_value2update = 4,
                                      pb_log = b_log)
# Update ECOWEIGHT input-file with tbl_input_statement_calving[5,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[5,1]),
                                      ps_statement2search = tbl_input_statement_calving[5,2],
                                      ps_value2update = 3,
                                      pb_log = b_log)
```


# Calculate calving score proportions

```{r}
# Calving score proportion for primiparous, a specific sire breed, female, calving score 2
calvingscore_prop_prim_F_2 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "F",
                                                                ps_calvingscore = 2,
                                                                pb_log = b_log)
calvingscore_prop_prim_F_2
# Calving score proportion for primiparous, a specific sire breed, female, calving score 3
calvingscore_prop_prim_F_3 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "F",
                                                                ps_calvingscore = 3,
                                                                pb_log = b_log)
calvingscore_prop_prim_F_3
# Calving score proportion for primiparous, a specific sire breed, female, calving score 4
calvingscore_prop_prim_F_4 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "F",
                                                                ps_calvingscore = 4,
                                                                pb_log = b_log)
calvingscore_prop_prim_F_4
```

```{r}
# Calving score proportion for multiparous, a specific sire breed, female, calving score 2
calvingscore_prop_multi_F_2 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "F",
                                                                 ps_calvingscore = 2,
                                                                 pb_log = b_log)
calvingscore_prop_multi_F_2
# Calving score proportion for multiparous, a specific sire breed, female, calving score 3
calvingscore_prop_multi_F_3 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "F",
                                                                 ps_calvingscore = 3,
                                                                 pb_log = b_log)
calvingscore_prop_multi_F_3
# Calving score proportion for multiparous, a specific sire breed, female, calving score 4
calvingscore_prop_multi_F_4 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "F",
                                                                 ps_calvingscore = 4,
                                                                 pb_log = b_log)
calvingscore_prop_multi_F_4
```

```{r}
# Build a vector with 10 lactations for calving score 2 proportion for females
value2update_calvingscoreprop_prim_F_2 <- paste0(c(calvingscore_prop_prim_F_2, rep(calvingscore_prop_multi_F_2,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[6,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[6,1]),
                                      ps_statement2search = tbl_input_statement_calving[6,2],
                                      ps_value2update = value2update_calvingscoreprop_prim_F_2,
                                      pb_log = b_log)
# Build a vector with 10 lactations for calving score 3 proportion for females
value2update_calvingscoreprop_prim_F_3 <- paste0(c(calvingscore_prop_prim_F_3, rep(calvingscore_prop_multi_F_3,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[7,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[7,1]),
                                      ps_statement2search = tbl_input_statement_calving[7,2],
                                      ps_value2update = value2update_calvingscoreprop_prim_F_3,
                                      pb_log = b_log)
# Build a vector with 10 lactations for calving score 4 proportion for females
value2update_calvingscoreprop_prim_F_4 <- paste0(c(calvingscore_prop_prim_F_4, rep(calvingscore_prop_multi_F_4,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[8,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[8,1]),
                                      ps_statement2search = tbl_input_statement_calving[8,2],
                                      ps_value2update = value2update_calvingscoreprop_prim_F_4,
                                      pb_log = b_log)
```


```{r}
# Calving score proportion for primiparous, a specific sire breed, male, calving score 2
calvingscore_prop_prim_M_2 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "M",
                                                                ps_calvingscore = 2,
                                                                pb_log = b_log)
calvingscore_prop_prim_M_2
# Calving score proportion for primiparous, a specific sire breed, male, calving score 3
calvingscore_prop_prim_M_3 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "M",
                                                                ps_calvingscore = 3,
                                                                pb_log = b_log)
calvingscore_prop_prim_M_3
# Calving score proportion for primiparous, a specific sire breed, male, calving score 4
calvingscore_prop_prim_M_4 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "M",
                                                                ps_calvingscore = 4,
                                                                pb_log = b_log)
calvingscore_prop_prim_M_4
```

```{r}
# Calving score proportion for multiparous, a specific sire breed, male, calving score 2
calvingscore_prop_multi_M_2 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "M",
                                                                 ps_calvingscore = 2,
                                                                 pb_log = b_log)
calvingscore_prop_multi_M_2
# Calving score proportion for multiparous, a specific sire breed, male, calving score 3
calvingscore_prop_multi_M_3 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "M",
                                                                 ps_calvingscore = 3,
                                                                 pb_log = b_log)
calvingscore_prop_multi_M_3
# Calving score proportion for multiparous, a specific sire breed, male, calving score 4
calvingscore_prop_multi_M_4 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "M",
                                                                 ps_calvingscore = 4,
                                                                 pb_log = b_log)
calvingscore_prop_multi_M_4
```

```{r}
# Build a vector with 10 lactations for calving score 2 proportion for males
value2update_calvingscoreprop_prim_M_2 <- paste0(c(calvingscore_prop_prim_M_2, rep(calvingscore_prop_multi_M_2,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[9,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[9,1]),
                                      ps_statement2search = tbl_input_statement_calving[9,2],
                                      ps_value2update = value2update_calvingscoreprop_prim_M_2,
                                      pb_log = b_log)
# Build a vector with 10 lactations for calving score 3 proportion for males
value2update_calvingscoreprop_prim_M_3 <- paste0(c(calvingscore_prop_prim_M_3, rep(calvingscore_prop_multi_M_3,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[10,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[10,1]),
                                      ps_statement2search = tbl_input_statement_calving[10,2],
                                      ps_value2update = value2update_calvingscoreprop_prim_M_3,
                                      pb_log = b_log)
# Build a vector with 10 lactations for calving score 4 proportion for males
value2update_calvingscoreprop_prim_M_4 <- paste0(c(calvingscore_prop_prim_M_4, rep(calvingscore_prop_multi_M_4,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[11,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[11,1]),
                                      ps_statement2search = tbl_input_statement_calving[11,2],
                                      ps_value2update = value2update_calvingscoreprop_prim_M_4,
                                      pb_log = b_log)
```


# Calculate proportion of calves died into 24 hours

```{r}
# Proportion of calves died into 24 hours for primiparous and easy calving (calving scores 1 and 2)
calvingdied24h_prop_prim_easy <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                            ps_statement_firstlactation = TRUE,
                                                                            ps_statement_easycalving = TRUE,
                                                                            pb_log = b_log)
calvingdied24h_prop_prim_easy
# Proportion of calves died into 24 hours for multiparous and easy calving (calving scores 1 and 2)
calvingdied24h_prop_multi_easy <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                             ps_statement_firstlactation = FALSE,
                                                                             ps_statement_easycalving = TRUE,
                                                                             pb_log = b_log)
calvingdied24h_prop_multi_easy
```
```{r}
# if proportion of calves died into 24 hours = 0, then set a default value coming from the internship of Jessica
  if(calvingdied24h_prop_prim_easy == 0){
    calvingdied24h_prop_prim_easy <- unlist(strsplit(tbl_input_statement_calving[13,4]$input_value, split = " "))[1]
  }
  if(calvingdied24h_prop_multi_easy == 0){
    calvingdied24h_prop_multi_easy <- unlist(strsplit(tbl_input_statement_calving[13,4]$input_value, split = " "))[2]
  }
```

```{r}
# Build a vector with 10 lactations for proportion of calves died into 24 hours and easy calving
value2update_calvingdied24hprop_easy <- paste0(c(calvingdied24h_prop_prim_easy, rep(calvingdied24h_prop_multi_easy,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[13,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[13,1]),
                                      ps_statement2search = tbl_input_statement_calving[13,2],
                                      ps_value2update = value2update_calvingdied24hprop_easy,
                                      pb_log = b_log)

```

```{r}
# Proportion of calves died into 24 hours for primiparous and difficult calving (calving scores 3 and 4)
calvingdied24h_prop_prim_difficult <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                         ps_statement_firstlactation = TRUE,
                                                                         ps_statement_easycalving = FALSE,
                                                                         pb_log = b_log)
calvingdied24h_prop_prim_difficult
# Proportion of calves died into 24 hours for multiparous and difficult calving (calving scores 3 and 4)
calvingdied24h_prop_multi_difficult <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                          ps_statement_firstlactation = FALSE,
                                                                          ps_statement_easycalving = FALSE,
                                                                          pb_log = b_log)
calvingdied24h_prop_multi_difficult
```

```{r}
# if proportion of calves died into 24 hours = 0, then set a default value coming from the internship of Jessica
  if(calvingdied24h_prop_prim_difficult == 0){
    calvingdied24h_prop_prim_difficult <- unlist(strsplit(tbl_input_statement_calving[12,4]$input_value, split = " "))[1]
  }
  if(calvingdied24h_prop_multi_difficult == 0){
    calvingdied24h_prop_multi_difficult <- unlist(strsplit(tbl_input_statement_calving[12,4]$input_value, split = " "))[2]
  }
```

```{r}
# Build a vector with 10 lactations for proportion of calves died into 24 hours and difficult calving
value2update_calvingdied24hprop_difficult <- paste0(c(calvingdied24h_prop_prim_difficult, rep(calvingdied24h_prop_multi_difficult,9)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[12,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[12,1]),
                                      ps_statement2search = tbl_input_statement_calving[12,2],
                                      ps_value2update = value2update_calvingdied24hprop_difficult,
                                      pb_log = b_log)

```

# Losses of calves from 48 hours after calving

```{r}
calf_loss <- calculate_calvesdiedafter24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                     pb_log = b_log)
```

```{r}
# Update ECOWEIGHT input-file with tbl_input_statement_calving[14,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[14,1]),
                                      ps_statement2search = tbl_input_statement_calving[14,2],
                                      ps_value2update = calf_loss,
                                      pb_log = b_log)

```

# Defining proportion of cows artificially inseminated in first oestrus

```{r}
# Build a vector with 10 lactations of proportion of cows with dystocia that were artificially inseminated for first oestrus (1 = all cows initially inseminated with AI)
dystocia_AI <- paste0(c(rep(1,10)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[15,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[15,1]),
                                      ps_statement2search = tbl_input_statement_calving[15,2],
                                      ps_value2update = dystocia_AI,
                                      pb_log = b_log)

# Build a vector with 10 lactations of proportion of cows without dystocia that were artificially inseminated for first oestrus (1 = all cows initially inseminated with AI)
easy_AI <- paste0(c(rep(1,10)),collapse = " ")
# Update ECOWEIGHT input-file with tbl_input_statement_calving[16,]
update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_dambreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[16,1]),
                                      ps_statement2search = tbl_input_statement_calving[16,2],
                                      ps_value2update = easy_AI,
                                      pb_log = b_log)
```

