---
title: "Manual pre-process EWBC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, you will get more information about the construction of the main-function `pre_process_ewbc_input()`. The task of this function is to pre-process the input-parameter-files of ECOWEIGHT for beef cattle (EWBC).

# Parameters

The parameters needed are:

```{r}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "2"
# Marketing channel can be: Natura-Beef, SwissPrimBeef
s_marketingchannel <- "Natura-Beef"
# Path to define from the working directory
s_path_directory2create <- file.path(here::here(),"inst","extdata","ewbc")
# Path to input from the literature research. Based on this example an other file can be created with different input-value and input-source.
s_input_file_literature <- file.path(here::here(),"inst","extdata","ewbc","input_literature.txt")
# Path to input from the parameter specific for the scenario. Based on this example an other file can be created with different input-value.
s_input_file_par <- file.path(here::here(),"inst","extdata","ewbc","input_par_statement.txt")
# Path to input from the calving. Based on this example an other file can be created with different input-values.
s_input_file_calving_statement <- file.path(here::here(),"inst","extdata","ewbc","input_calving_statement.txt")
# Path to calving data file
s_input_file_calving <- file.path(here::here(),"inst","extdata","ewbc","test","test_zws_muku_gal.csv")
# Date YYYYMMDD used as start date to filter data for calving or carcass
s_start_date <- 20160101
# Date YYYYMMDD used as end date to filter data for calving or carcass
s_end_date <- 20211231
# Path to input from the progeny flp data. Based on this example an other file can be created with different input-values.
s_input_file_progeny_flp_statement <- file.path(here::here(),"inst","extdata","ewbc","input_flp_statement.txt")
# Path to flp data file
s_input_file_flp <- file.path(here::here(),"inst","extdata","ewbc","test","test_zws_muku_flp.csv")
# Path to input statement for carcass and price
s_input_file_flp_carcass_matrix_statement <- file.path(here::here(),"inst","extdata","ewbc","input_flp_carcass_matrix_statement.txt")
# Path to input with cow price. Based on this example an other file can be created with different input-values.
s_input_file_price_cow <- file.path(here::here(),"inst","extdata","ewbc","cow_price.txt")
# Path to input with bull price. Based on this example an other file can be created with different input-values.
s_input_file_price_bull <- file.path(here::here(),"inst","extdata","ewbc","bull_price.txt")
# Path to input with heifer price. Based on this example an other file can be created with different input-values.
s_input_file_price_heifer <- file.path(here::here(),"inst","extdata","ewbc","heifer_price.txt")
# Flag to set to TRUE, if a log-file is whished
b_log <- TRUE
```

# Logfile

At the beginning of the function depending of the setting for `pb_log` and `plogger`, a log-file will be created.

# Major steps of pre_process_ewbc_input() are

 1) function `create_directory_scenario()` : create directory per scenario with input-parameter-file for ECOWEIGHT. Details in the vignette Explain the function create_directory_scenario().
 
 2) Read file with input from literature research and update input-parameter-file coming from literature of ECOWEIGHT. Details in the vignette Explain the part only from literature.
 
 3) function `pre_process_ew_input_calving()` : Pre-processing the calving data for input-parameter-file of ECOWEIGHT. Details in the vignette Explain the function pre_process_ew_input_calving().
 
 4) function `pre_process_ewbc_input_progeny_data_flp()` : Pre-processing the progeny data flp for input-parameter-file of ECOWEIGHT. Details in the vignette Explain the function pre_process_ew_input_progeny_data_flp(). 
 
 5) function `pre_process_ew_input_carcass_data_flp()` : Pre-processing the carcass conformation, fat, prices based on flp-data for input-parameter-file of ECOWEIGHT. Details in the vignette Explain the function pre_process_ew_input_carcass_data_flp().

# Run pre_process_ewbc_input() in RStudio

```{r, warning=FALSE, message=FALSE}
pre_process_ewbc_input(ps_sirebreed = s_sirebreed,
                       ps_prodsystew = s_prodsystew,
                       ps_marketchannel = s_marketingchannel,
                       ps_path_directory2create = s_path_directory2create,
                       ps_input_file_literature = s_input_file_literature,
                       ps_input_file_par = s_input_file_par,
                       ps_input_file_calving_statement = s_input_file_calving_statement,
                       ps_input_file_calving = s_input_file_calving,
                       ps_start_date = s_start_date,
                       ps_end_date = s_end_date,
                       ps_input_file_progeny_flp_statement = s_input_file_progeny_flp_statement,
                       ps_input_file_flp = s_input_file_flp,
                       ps_input_file_flp_carcass_matrix_statement = s_input_file_flp_carcass_matrix_statement,
                       ps_input_file_price_cow = s_input_file_price_cow,
                       ps_input_file_price_bull = s_input_file_price_bull,
                       ps_input_file_price_heifer = s_input_file_price_heifer,
                       pb_log = b_log)
```


```{r}
cat(rmdhelp::get_latest_change())
```

