---
title: "Testing the function pre_process_ew_input_calving()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explain the function pre_process_ew_input_calving()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Aim

In this vignette, we will try to build unit tests for the differrent sub-function of `pre_process_ew_input_calving()`. 

# Prepare test-read_file_input_calving.R

```{r}
s_input_file_calving <- file.path(here::here(),"inst","extdata","test","test_zws_muku_gal.csv")
s_start_calving_date <- 20150101
s_end_calving_date <- 20220504
b_log <- TRUE
tbl_calving <- read_file_input_calving(ps_input_file_calving = s_input_file_calving,
                                       ps_start_calving_date = s_start_calving_date,
                                       ps_end_calving_date = s_end_calving_date,
                                       pb_log = b_log)
#Write output to use in test-read_file_input_calving.R
readr::write_delim(tbl_calving, file = file.path(here::here(),"inst","extdata","test","test_tbl_calving.csv"), delim = ";")
```

```{r}
s_output_file_calving <- file.path(here::here(),"inst","extdata","test","test_tbl_calving.csv")
tbl_output_file_calving <- readr::read_delim(file = s_output_file_calving, delim = ";")
```

# Prepare test-calculate_abortion_rate.R

```{r}
# Abortion rate for primiparous
abortrate_prim <- calculate_abortion_rate(ps_input_calving_tibble = tbl_calving,
                                          ps_statement_firstlactation = TRUE,
                                          pb_log = b_log)
# Set variable abortrate_prim in test_calculate_abortion_rate.R as expected value
# Abortion rate for multiparous
abortrate_multi <- calculate_abortion_rate(ps_input_calving_tibble = tbl_calving,
                                           ps_statement_firstlactation = FALSE,
                                           pb_log = b_log)
# Set variable abortrate_multi in test_calculate_abortion_rate.R as expected value
# Build a vector with 10 lactations for abortion rate
value2update_abortrate <- paste0(c(abortrate_prim, rep(abortrate_multi,9)),collapse = " ")
```

# Prepare test-update_input_parameter_file.R for aboration rate

```{r}
# Read Statements
s_input_file_calving_statement <- file.path(here::here(),"inst","extdata","input_calving_statement.txt")
tbl_input_statement_calving <- read_file_input(ps_input_file = s_input_file_calving_statement,
                                               pb_log = b_log)
```

```{r}
s_path_directory2create <- "/Users/skn/muku_Ecoweigth/2022/prog/qp4ewc/inst/extdata/test/"
s_sirebreed <- "LM"
s_prodsystew <- "2"
s_marketingchannel <- "Natura-Beef"
s_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[1,1])
s_statement2search = tbl_input_statement_calving[1,2]
s_value2update = value2update_abortrate

## Update ECOWEIGHT input-file with the calculated abortion rates in tbl_input_statement_calving[1,]
#update_input_parameter_file(ps_path2template_input_parameter_file = #file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[1,1]),
#                                      ps_statement2search = tbl_input_statement_calving[1,2],
#                                      ps_value2update = value2update_abortrate,
#                                      pb_log = b_log)
```

# Prepare test-calculate_stillbirth_rate.R for stillbirth rate

```{r}
# stillbirth rate for easy calving (calving scores 1 and 2)
# for primiparous  
stillbirthrate_prim_easy <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                      ps_statement_firstlactation = TRUE,
                                                      ps_statement_easycalving = TRUE,
                                                      pb_log = b_log)
# for multiparous
stillbirthrate_multi_easy <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                       ps_statement_firstlactation = FALSE,
                                                       ps_statement_easycalving = TRUE,
                                                       pb_log = b_log)
# Build a vector with 10 lactations for stillbirth rate
value2update_stillbirthrate_easy <- paste0(c(stillbirthrate_prim_easy, rep(stillbirthrate_multi_easy,9)),collapse = " ")
```

```{r}
# stillbirth rate for difficult calving (calving scores 3 and 4)
# for primiparous 
stillbirthrate_prim_difficult <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                           ps_statement_firstlactation = TRUE,
                                                           ps_statement_easycalving = FALSE,
                                                           pb_log = b_log)
# for multiparous
stillbirthrate_multi_difficult <- calculate_stillbirth_rate(ps_input_calving_tibble = tbl_calving,
                                                            ps_statement_firstlactation = FALSE,
                                                            ps_statement_easycalving = FALSE,
                                                            pb_log = b_log)
value2update_stillbirthrate_difficult <- paste0(c(stillbirthrate_prim_difficult, rep(stillbirthrate_multi_difficult,9)),collapse = " ")
```


# Prepare test-calculate_calvingscore_proportion.R

```{r}
# Calving score proportion for primiparous, a specific sire breed, female, calving score 2
calvingscore_prop_prim_F_2 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "F",
                                                                ps_calvingscore = 2,
                                                                pb_log = b_log)
# Calving score proportion for multiparous, a specific sire breed, female, calving score 2
calvingscore_prop_multi_F_2 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "F",
                                                                 ps_calvingscore = 2,
                                                                 pb_log = b_log)
# Build a vector with 10 lactations for calving score 2 proportion for females
value2update_calvingscoreprop_prim_F_2 <- paste0(c(calvingscore_prop_prim_F_2, rep(calvingscore_prop_multi_F_2,9)),collapse = " ")
```

```{r}
# Calving score proportion for primiparous, a specific sire breed, male, calving score 3
calvingscore_prop_prim_M_3 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                ps_statement_firstlactation = TRUE,
                                                                ps_breed = s_sirebreed,
                                                                ps_sex = "M",
                                                                ps_calvingscore = 3,
                                                                pb_log = b_log)
# Calving score proportion for multiparous, a specific sire breed, male, calving score 3
calvingscore_prop_multi_M_3 <- calculate_calvingscore_proportion(ps_input_calving_tibble = tbl_calving,
                                                                 ps_statement_firstlactation = FALSE,
                                                                 ps_breed = s_sirebreed,
                                                                 ps_sex = "M",
                                                                 ps_calvingscore = 3,
                                                                 pb_log = b_log)
# Build a vector with 10 lactations for calving score 3 proportion for males
value2update_calvingscoreprop_prim_M_3 <- paste0(c(calvingscore_prop_prim_M_3, rep(calvingscore_prop_multi_M_3,9)),collapse = " ")
```

# Prepare test-calculate_calvesdied24h_proportion.R

```{r}
# Proportion of calves died into 24 hours for primiparous and easy calving (calving scores 1 and 2)
calvingdied24h_prop_prim_easy <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                            ps_statement_firstlactation = TRUE,
                                                                            ps_statement_easycalving = TRUE,
                                                                            pb_log = b_log)
# Proportion of calves died into 24 hours for multiparous and easy calving (calving scores 1 and 2)
calvingdied24h_prop_multi_easy <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                             ps_statement_firstlactation = FALSE,
                                                                             ps_statement_easycalving = TRUE,
                                                                             pb_log = b_log)
value2update_calvingdied24hprop_easy <- paste0(c(calvingdied24h_prop_prim_easy, rep(calvingdied24h_prop_multi_easy,9)),collapse = " ")
```

```{r}
# Proportion of calves died into 24 hours for primiparous and difficult calving (calving scores 3 and 4)
calvingdied24h_prop_prim_difficult <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                         ps_statement_firstlactation = TRUE,
                                                                         ps_statement_easycalving = FALSE,
                                                                         pb_log = b_log)
# Proportion of calves died into 24 hours for multiparous and difficult calving (calving scores 3 and 4)
calvingdied24h_prop_multi_difficult <- calculate_calvesdied24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                                          ps_statement_firstlactation = FALSE,
                                                                          ps_statement_easycalving = FALSE,
                                                                          pb_log = b_log)
# Build a vector with 10 lactations for proportion of calves died into 24 hours and difficult calving
value2update_calvingdied24hprop_difficult <- paste0(c(calvingdied24h_prop_prim_difficult, rep(calvingdied24h_prop_multi_difficult,9)),collapse = " ")

```

# Prepare test-calculate_calvesdiedafter24h_proportion.R

```{r}
calf_loss <- calculate_calvesdiedafter24h_proportion(ps_input_calving_tibble = tbl_calving,
                                                     pb_log = b_log)
```
