---
title: "Debugging pre-process EWBC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Debugging}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qp4ewc)
```

# Parameters

The parameters needed are:

```{r}
# Sire breed can be: AN,AU,CH,LM,OB,SI corresponding to Angus,Aubrac, Charolais, Limousin, Original-Braunvieh, Simmental
s_sirebreed <- "LM"
# Production system according to ECOWEIGHT: 1,2,3,4 corresponding to purebreeding, crossbreeding, terminal crossing, dairy
s_prodsystew <- "3"
# Marketing channel can be: Natura-Beef, SwissPrimBeef
s_marketingchannel <- "Natura-Beef"
# Path to define from the working directory
s_path_directory2create <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/work"
# Path to input from the literature research. Based on this example an other file can be created with different input-value and input-source.
s_input_file_literature <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/input_literature_ewbc.txt"
# Path to input from the parameter specific for the scenario. Based on this example an other file can be created with different input-value.
s_input_file_par <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/input_par_statement_ewbc.txt"
# Path to input from the calving. Based on this example an other file can be created with different input-values.
s_input_file_calving_statement <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/input_calving_statement_ewbc.txt"
# Path to calving data file
s_input_file_calving <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/work/zws_muku_gal.csv"
# Date YYYYMMDD used as start date to filter data for calving or carcass
s_start_date <- 20160101
# Date YYYYMMDD used as end date to filter data for calving or carcass
s_end_date <- 20211231
# Path to input from the progeny flp data. Based on this example an other file can be created with different input-values.
s_input_file_progeny_flp_statement <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/input_flp_statement_ewbc.txt"
# Path to flp data file
s_input_file_flp <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/work/zws_muku_flp.csv"
# Path to input statement for carcass and price
s_input_file_flp_carcass_matrix_statement <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/input_flp_carcass_matrix_statement_ewbc.txt"
# Path to input with cow price. Based on this example an other file can be created with different input-values.
s_input_file_price_cow <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/cow_price_ewbc.txt"
# Path to input with bull price. Based on this example an other file can be created with different input-values.
s_input_file_price_bull <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/bull_price_ewbc.txt"
# Path to input with heifer price. Based on this example an other file can be created with different input-values.
s_input_file_price_heifer <- "/Users/skn/muku_Ecoweigth/2022/test_pipeline/par/heifer_price_ewbc.txt"
# Flag to set to TRUE, if a log-file is whished
b_log <- FALSE
```

# Major steps of pre_process_ewbc_input() are

 1) function `create_directory_scenario()` : create directory per scenario with input-parameter-file for ECOWEIGHT. Details in the vignette Explain the function create_directory_scenario().
 
```{r}
create_directory_scenario(s_sirebreed,
                          s_prodsystew,
                          s_marketingchannel,
                          s_path_directory2create,
                          pb_log = b_log,
                          plogger = NULL)
```

 2) Read file with input from literature research and update input-parameter-file coming from literature of ECOWEIGHT. Details in the vignette Explain the part only from literature.
 
```{r}
tbl_input_literature <- qp4ewc::read_file_input(s_input_file_literature,
                                                pb_log = b_log,
                                                plogger = NULL)

```

```{r}
  for(l in 1:nrow(tbl_input_literature)){
    update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_literature[l,1]),
                                        ps_statement2search = tbl_input_literature[l,2],
                                        ps_value2update = tbl_input_literature[l,4]$input_value,
                                        pb_log= b_log,
                                        plogger = NULL)
  }
```

```{r}
tbl_input_par <- read_file_input(s_input_file_par,
                                 pb_log= b_log,
                                 plogger = NULL)
```

```{r}
  for(l in 1:nrow(tbl_input_par)){
    update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_par[l,1]),
                                        ps_statement2search = tbl_input_par[l,2],
                                        ps_value2update = tbl_input_par[l,4]$input_value,
                                        pb_log= b_log,
                                        plogger = NULL)
  }
```

 3) function `pre_process_ew_input_calving()` : Pre-processing the calving data for input-parameter-file of ECOWEIGHT. Details in the vignette Explain the function pre_process_ew_input_calving().
 
```{r}
tbl_input_statement_calving <- read_file_input(s_input_file_calving_statement,
                                               pb_log= b_log,
                                               plogger = NULL)
```

```{r}
tbl_calving <- read_file_input_calving(s_input_file_calving,
                                       s_start_date,
                                       s_end_date,
                                       pb_log= b_log,
                                       plogger = NULL)
```

```{r}
abortrate_prim <- calculate_abortion_rate(ps_input_calving_tibble = tbl_calving,
                                                  ps_statement_firstlactation = TRUE,
                                                  pb_log= b_log,
                                                  plogger = NULL)
  if(abortrate_prim == 0){
    abortrate_prim <- unlist(strsplit(tbl_input_statement_calving[1,4]$input_value, split = " "))[1]
  }
  abortrate_multi <- qp4ewc::calculate_abortion_rate(ps_input_calving_tibble = tbl_calving,
                                                     ps_statement_firstlactation = FALSE,
                                                     pb_log= b_log,
                                                     plogger = NULL)
  # Check if abortrate_multi is zero. If it is the case, set a default value
  if(abortrate_multi == 0){
    abortrate_multi <- unlist(strsplit(tbl_input_statement_calving[1,4]$input_value, split = " "))[2]
  }
  value2update_abortrate <- paste0(c(abortrate_prim, rep(abortrate_multi,9)),collapse = " ")
  qp4ewc::update_input_parameter_file(ps_path2template_input_parameter_file = file.path(s_path_directory2create,paste0(s_sirebreed,"_",s_prodsystew,"_",s_marketingchannel),tbl_input_statement_calving[1,1]),
                                      ps_statement2search = tbl_input_statement_calving[1,2],
                                      ps_value2update = value2update_abortrate,
                                      pb_log= b_log,
                                      plogger = NULL)
```

 
 4) function `pre_process_ewbc_input_progeny_data_flp()` : Pre-processing the progeny data flp for input-parameter-file of ECOWEIGHT. Details in the vignette Explain the function pre_process_ew_input_progeny_data_flp(). 
 
 5) function `pre_process_ew_input_carcass_data_flp()` : Pre-processing the carcass conformation, fat, prices based on flp-data for input-parameter-file of ECOWEIGHT. Details in the vignette Explain the function pre_process_ew_input_carcass_data_flp().

# Run pre_process_ewbc_input() in RStudio

```{r, warning=FALSE, message=FALSE}
pre_process_ewbc_input(ps_sirebreed = s_sirebreed,
                       ps_prodsystew = s_prodsystew,
                       ps_marketchannel = s_marketingchannel,
                       ps_path_directory2create = s_path_directory2create,
                       ps_input_file_literature = s_input_file_literature,
                       ps_input_file_par = s_input_file_par,
                       ps_input_file_calving_statement = s_input_file_calving_statement,
                       ps_input_file_calving = s_input_file_calving,
                       ps_start_date = s_start_date,
                       ps_end_date = s_end_date,
                       ps_input_file_progeny_flp_statement = s_input_file_progeny_flp_statement,
                       ps_input_file_flp = s_input_file_flp,
                       ps_input_file_flp_carcass_matrix_statement = s_input_file_flp_carcass_matrix_statement,
                       ps_input_file_price_cow = s_input_file_price_cow,
                       ps_input_file_price_bull = s_input_file_price_bull,
                       ps_input_file_price_heifer = s_input_file_price_heifer,
                       pb_log = b_log)
```
